### 2016-12-01 Projects/DelCo_2012/Report/DelCo_2012.tex
update acknowledgements to CAF report

@@

Thanks to all involved for assisting in generating data that will aid the fire service in making evidence based tactical choices.

>>>>

This study was part of a larger DHS/FEMA Assistance to Firefighters Research and Development Grant project led by California Polytechnic State University (Cal Poly), San Luis Obispo. The authors would like to acknowledge the support of the Cal Poly team, especially: Fred Mowrer, Christopher Dicus, Thomas Korman and Sean Mitchell.

@@

Thanks to all involved for assisting in generating data that will aid the fire service in making evidence based tactical choices. A special thanks to Joseph Scheffey of Jensen Hughes and Nelson Bryner of NIST for a thorough technical review of this manuscript.
